Verifying Demonstrations

### 2018-11-15 paper/analysis-performance.tex
s/PRIVO/CROCUS/g

\subsection{Smartphones, smartcards}
Performance considerations are crucial during the protests due to the nature of the devices used to run \PRIVO, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity. 
Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
For instance, benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in \SI{153}{\milli\second}. 
However, those benchmarks also demonstrate that smartcards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). 
While the limited processing power of many embarked systems has been a challenge, Idemix has been successfully implemented to prove the possession of credentials on Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation ``suitable for real life transactions''~\cite{IRMA} while maintaining security and privacy for its users.

\subsection{Distance bounding anonymous credentials}
With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated. The first step is only done once and is fairly costly in terms of ressources. 
This means that the best strategy is to precompute the corresponding results and to store them on the prover's device. 
This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol [1].
%Seb: to do add the reference to the following paper at the end of the sentence:
%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
Considering the entire setup of our protocol, we perform 7 random number generations (one of them being a single bit), two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$). 
This can be reduced to 4 random number generations and one exponentiation using precomputation. The Anon-pass article [2] gives us a total time of 43,2 milliseconds of raw protocol operation time in order to create, sign and verify a given message (the registration phase), and then 21,4 mililseconds to login.
%[2] Lee, M., Dunn, A., Katz, J., Waters, B., & Witchel, E. (2013). Anon-pass: Practical anonymous
%subscriptions. IEEE Security & Privacy, (1), 1.

>>>>

\subsection{Smartphones, smartcards}
Performance considerations are crucial during the protests due to the nature of the devices used to run \CROCUS, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity. 
Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
For instance, benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in \SI{153}{\milli\second}. 
However, those benchmarks also demonstrate that smartcards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). 
While the limited processing power of many embarked systems has been a challenge, Idemix has been successfully implemented to prove the possession of credentials on Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation ``suitable for real life transactions''~\cite{IRMA} while maintaining security and privacy for its users.

% \subsection{Distance bounding anonymous credentials}
% With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated. The first step is only done once and is fairly costly in terms of ressources. 
% This means that the best strategy is to precompute the corresponding results and to store them on the prover's device. 
% This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol [1].
%Seb: to do add the reference to the following paper at the end of the sentence:
%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
Considering the entire setup of our protocol, we perform 7 random number generations (one of them being a single bit), two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$). 
% This can be reduced to 4 random number generations and one exponentiation using precomputation. The Anon-pass article [2] gives us a total time of 43,2 milliseconds of raw protocol operation time in order to create, sign and verify a given message (the registration phase), and then 21,4 mililseconds to login.
%[2] Lee, M., Dunn, A., Katz, J., Waters, B., & Witchel, E. (2013). Anon-pass: Practical anonymous
%subscriptions. IEEE Security & Privacy, (1), 1.

### 2018-11-15 paper/analysis-security.tex
Fixes Syntastic warnings
Bugfix: \include doesn't want .tex suffix
s/PRIVO/CROCUS/g

@@

\subsection{Eligibility verifiability}
\label{analysis-eligibility}

\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
In \PRIVO, we have several attributes that must be verifiable: the time of creation (\ie, temporal eligibility), the physical location of \(\sk_P\) at creation (\ie, spatial eligibility), recognition of two proofs originating from the same person (\ie, one-proof-per-person eligibility) and that the proof is indeed designated for the event (\ie, designated-event eligibility).
We will now analyze these properties.

\paragraph{Temporal eligibility}
\label{analysis-temporal}

@@

\paragraph{Linkability}
\label{analysis-linkability}

@@

\paragraph{Spatial eligibility}
\label{analysis-spatial}

@@

\paragraph{Designated protest}
\label{analysis-designated}

@@

>>>>

\sonja{including adversary model with different levels here for now as
  it already contains some security analysis}
\daniel{moved it to the top}
\input{adversary-model.tex}

@@

\subsection{Eligibility verifiability}%
\label{analysis-eligibility}

\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
In \CROCUS, we have several attributes that must be verifiable: the time of creation (\ie, temporal eligibility), the physical location of \(\sk_P\) at creation (\ie, spatial eligibility), recognition of two proofs originating from the same person (\ie, one-proof-per-person eligibility) and that the proof is indeed designated for the event (\ie, designated-event eligibility).
We will now analyze these properties.

\paragraph{Temporal eligibility}%
\label{analysis-temporal}

@@

\paragraph{Linkability}%
\label{analysis-linkability}

@@

\paragraph{Spatial eligibility}%
\label{analysis-spatial}

@@

\paragraph{Designated protest}%
\label{analysis-designated}

@@

\sonja{anonymity and cause unlinkability missing}

### 2018-11-15 paper/conclusions.tex
s/PRIVO/CROCUS/g

In this paper, we have introduced \PRIVO, a privacy-preserving protocol for verifiably counting participants at protests. 
Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests. }
With respect to privacy, \PRIVO provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \PRIVO).

Of separate interest, we have also built distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.

In general, none of the related works fulfills the eligibility
verifiability (one proof per person, temporal and spatial eligibility ---
\cref{%
  CountOnce,%
  TemporallyRelated,SpatiallyRelated,%
}).
To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
Moreover, if they provided individual verifiability, they would likely violate 
the privacy requirements --- if people must recognize themselves in photos, 
others can recognize them too.
Finally, most of the current methods are estimates, with quite some error margins. 
While \PRIVO is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol. 
Owing to the network effect, until used by most participants, \PRIVO would result in a considerable undercount. 
However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic. 
While the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies. We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes.

>>>>

In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests. 
Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
%To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
%Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests. }
%With respect to privacy, \PRIVO provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \PRIVO).
\sonja{update sec analysis results}

%Of separate interest, we have also built distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
%All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
%With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.

In general, none of the related works fulfills the eligibility
verifiability (one proof per person, temporal and spatial eligibility ---
\cref{%
  CountOnce,%
  TemporallyRelated,SpatiallyRelated,%
}).
To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
Moreover, if they provided individual verifiability, they would likely violate 
the privacy requirements --- if people must recognize themselves in photos, 
others can recognize them too.
Finally, most of the current methods are estimates, with quite some error margins. 
While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol. 
Owing to the network effect, until used by most participants, \CROCUS would result in a considerable undercount. 
However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic. 
While the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies. We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes.

### 2018-11-15 paper/intro.tex
s/PRIVO/CROCUS/g

\paragraph*{Contributions}

In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
%\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.}
%\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.

@@

The paper is organized as follows.
First, in \cref{system-model}, we formalize the notion of protest and define the desired verifiability properties.
We also present our system as well as the adversary model together with desired privacy properties.
Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \PRIVO. 
In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
%\daniel{Check that this is true before publication.} 
and formally verify it using Tamarin~\cite{TamarinDB}.
%Seb: we need to be careful about the above sentence
This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
Then \cref{Protocol}, we present \PRIVO, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}

>>>>

%\paragraph*{Contributions}

%In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.

% Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
% Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
% More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
% The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
%\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.}
%\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
%and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.

@@

The paper is organized as follows.
First, in \cref{system-model}, we formalize the notion of protest and define the desired verifiability properties.
We also present our system as well as the adversary model together with desired privacy properties.
Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS. 
In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
%Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
%We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
%\daniel{Check that this is true before publication.} 
%and formally verify it using Tamarin~\cite{TamarinDB}.
%Seb: we need to be careful about the above sentence
%This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
Then \cref{Protocol}, we present \PRIVO, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}
